Model to study co-evolution of trade an culture

### 2015-03-29 article.tex
finish result

\jm{stop for this evening}
where we see that the product or of the good blue found a good price for him but price that block the other product or to do well .

>>>>

In this graphic we can observe that the product displayed in green is blocked to a non-optimal value until iteration XXXX, and decreasing after. The prices for the blue product, on the other side, decrease steadily until the median reaches the uptimum at iteration XXXX. This illustrate the complexity of finding the right prices in the market. Indeed all prices are strongly linked together and until one has reach its optimum value, the other price can not evolve.
